\documentclass[]{../auvsi_doc}
\setkeys{../auvsi_doc.cls}{
	AUVSITitle={Capstone Team 45 Status Update 10-10-2018},
	AUVSILogoPath={./../logo.pdf}
}

\usepackage[toc,page]{appendix}

\begin{document}

\section{Goals for the Past Week}

The following is a list of our goals for the past week, as well as descriptions of their completion and/or progress:

\begin{enumerate}
\item \textbf{Finalize and ratify the Opportunity Development artifacts}\\
Attached is a compendium of our initial Opportunity Development artifacts. Together, they provide a basis for our chosen project requirements and key success measures.
\item \textbf{Be ready to fly a mock competition (minus the camera) on Thursday of next week}\\
Given unforseen snags and tasks to complete in recent days, we are limiting the scope of our first flight to flying RC and autonomous waypoints. This will occur on Friday, since we have a design review for capstone on Thursday.
\item \textbf{Continue testing pixel resolution of our camera at large target distances}
Our vision subteam got their hands on a 24 megapixel camera (compared with last year's 5 megapixel camera). We are currently performing tests with this camera to compare performance and determine whether it's worth it to run a faster computer onboard the UAV.
\end{enumerate}

\section{Goals for the Coming Week}

The following is a list of our goals for the coming week, as well as details about how we plan to accomplish them:

\begin{enumerate}
\item \textbf{Wrap up Opportunity Development stage}\\
Tomorrow during our design review, artifact changes pending, we plan on obtaining all the needed signatures to wrap up the Opportunity Development stage for capstone.
\item \textbf{Fly RC and autonomous waypoint capture in a test flight}\\
We plan to complete this on Friday, weather permitting. Tomorrow, we are performing a comprehensive pre-flight checklist to be ready for Friday.
\item \textbf{Register for the competition}\\
This entails filling out a google form and paying a \$1,000 fee after Sunday, October 14th. We can discuss the details of this with you in our Monday meeting.
\item \textbf{Get the Interop server serving up mock missions}\\
Currently, we have the Interop server running and communicating with the vision ground station. We still need to get the server communicating with the ROSplane groundstation and serving up actual mock missions.
\end{enumerate}

\textbf{Please send us any feedback with regards to the progress we've made, as well as our plans for the coming week.}

\end{document}
