\documentclass[]{../auvsi_doc}
\setkeys{../auvsi_doc.cls}{
	AUVSITitle={Capstone Team 45 Status Update 10-24-2018},
	AUVSILogoPath={./../logo.pdf}
}

\usepackage[toc,page]{appendix}

\begin{document}

\section{Goals for the Past Week}

The following is a list of our goals for the past week, as well as descriptions of their completion and/or progress:

\begin{enumerate}
\item \textbf{Begin documentation for the Concept Development stage}\\
Our design review is scheduled for next Friday, meaning that all of our artifacts (initial draft) are due one week from today. We have divided our needed artifacts into four different groups:
\begin{enumerate}
	\item Airframe
	\item Subsystem Interfaces
	\item UGV
	\item Vision
\end{enumerate}
Each group of artifacts has a pair of team members assigned to be principally responsible for them, and everyone has defined their own intermediate goals and plans to be ready by next Wednesday. 
\item \textbf{Patch up the plane and get more practice launching the plane while flying RC}\\
The vision subteam was able to accomplish this on their quest to obtain real image data for their concept selection. The plane crashed a second time (though after a slightly longer flight, this time around), and was patched up yet again.
\item \textbf{Find out what was causing the network connectivity issues at Tuesday's flight test}\\
During the test flight carried out by the vision subteam, it was discovered that the Ubiquity networking issues appear to be location-specific. As soon as they moved down a block, all issues with the network connection ceased. It is a little unsettling that connectivity would somehow be related to location, so we'll continue to keep our eyes open for this issue.
\item \textbf{Get last year's control and interop schemes up and running in simulation}\\
As of now, this goal will be postponed for next week, as we focus on preparing for the Concept Development design review.
\item \textbf{Run tests in a wind tunnel to evaluate our airspeed and barometer sensors}
As of now, this goal will be postponed for next week, as we focus on preparing for the Concept Development design review.
\end{enumerate}

\section{Goals for the Coming Week}

The following is a list of our goals for the coming week, as well as details about how we plan to accomplish them:

\begin{enumerate}
\item \textbf{Get ready for our Concept Development design review}\\
By this time next week, we plan to have all of our initial-draft Concept Development artifacts completed. We will ask for your input throughout the concept development process. Because this is such a large task, we will have no other major goals for completion this coming week.
\end{enumerate}

\textbf{Please send us any feedback with regards to the progress we've made, as well as our plans for the coming week.}

\end{document}
