\documentclass[]{../auvsi_doc}
\setkeys{../auvsi_doc.cls}{
	AUVSITitle={Capstone Team 45 Status Update 09-19-2018},
	AUVSILogoPath={./../logo.pdf}
}

% \setcounter{secnumdepth}{0}
\usepackage[toc,page]{appendix}

\begin{document}

\section{Goals for the Past Week}

The following is a list of our goals for the past week, as well as descriptions of their completion and/or progress:

\begin{enumerate}
\item \textbf{Complete and compile a rough draft of the Fall Camp Artifacts}\\
We were able to accomplish this goal, encompassed in the compiled Fall Camp Documents which we sent you. \textit{With the new competition rules that were released on Friday}, we will have to make significant adjustments to our conceptions of how to tackle the path planning and payload delivery requirements.
\item \textbf{Divide into subteams and assign preliminary roles}\\
We accomplished this goal. Specific roles were assigned to team members, as outlined in the Team Charter section of the Fall Camp Documents. Subteams were assigned, as outlined in appendix~\ref{appendix:subteamscharter}.
\item \textbf{Lay the groundwork for running a mock competition flight test with last year's competition setup}\\
We made progress toward this goal by doing the following:
\begin{itemize}
\item Having an hour-long meeting with Thane Downing about his experience with last year's competition, learning about the subsystems, and soliciting advice.
\item Transferring last year's competition hardware to the new projects lab in EB 112.
\item Completing part of the team-wide safety training for projects lab use.
\item Beginning taking inventory of and organizing last year's hardware.
\end{itemize}
Over the course of the next week, we plan on finishing taking inventory and organizing what we have in order to have a better idea of what we need to purchase.
\end{enumerate}

\section{Goals for the Coming Week}

The following is a list of our goals for the coming week, as well as details about how we plan to accomplish them:

\begin{enumerate}
\item \textbf{Define dates for design reviews and reports for the semester}\\
We plan on accomplishing this as a team tomorrow, which will be helpful for directing and prioritizing our efforts over the course of the semester.
\item \textbf{Redefine the design requirements for the Payload/Controls subteam}\\
Due to the new competition rules, we wish to remove our emphasis on designing a new path planner and placing emphasis on designing an unmanned ground vehicle for the payload requirement of the competition. This will result in a revised requirements matrix, as well as individual subteam requirements matrices.
\item \textbf{Construct a Team Contract}\\
We plan to accomplish this beginning with team-wide discussion, then splitting the documentation jobs between individual team members (with an executive editor to ensure consistency), allowing the rest of the team to focus on preparing for our mock competition.
\item \textbf{Complete the team safety training for projects lab use}\\
This will entail getting trained on how to use the PRL facilities on campus, as well as receiving a training from a member of the MAGICC lab on proper battery usage. We have set an appointment for each of these events in the coming week.
\item \textbf{Finish taking inventory of available hardware}
\item \textbf{Set an official date for running a mock competition flight test with last year's competition setup}
\end{enumerate}

\begin{appendices}

\section{Subteams Charter}
\label{appendix:subteamscharter}

Payload/Controls Group:
\begin{itemize}
\item Brady Moon
\item Ryan Anderson (Airframe Specialist)
\item John Akagi
\item Tyler Critchfield (Airframe)
\item Kameron Eves
\item Jacob Willis
\end{itemize}
Vision Group:
\begin{itemize}
\item Connor Olsen
\item Tyler Miller
\item Jake Johnson
\item Derek Knowles
\item Brandon McBride
\end{itemize}
An independent team lead:
\begin{itemize}
\item Andrew Torgesen
\end{itemize}

\end{appendices}

\end{document}
