\documentclass[]{../auvsi_doc}
\setkeys{../auvsi_doc.cls}{
	AUVSITitle={Capstone Team 45 Status Update 1-23-19},
	AUVSILogoPath={./../logo.pdf}
}
% ATOM BUILD: Ctrl+Alt+B
\usepackage[toc,page]{appendix}

\begin{document}

\section{Goals for the Past Week}

The following is a list of our goals for the past week, as well as descriptions of their completion and/or progress:

\begin{enumerate}
	\item \textbf{Tune the autopilot and airspeed estimator} (\textit{Brady, John, Andrew}) \\
	We plan on having the airspeed sensor fixed tomorrow, and we will also ensure that the RC transmitter can toggle autopilot functionality. We now have a working autopilot interface for controller tuning, so we should be able to tune the gains in the next week.
	\item \textbf{Get the path planner back to its previous glory} (\textit{Brady, John, Andrew}) \\
	Little progress has been made on this front, since we're focusing on getting the fundamentals of the controller working before we turn to obstacle avoidance.
	\item \textbf{Parachute deployment testing and iteration} (\textit{Jacob W., Derek, Brandon}) \\
	This remains to be done. A 36-inch parachute was ordered, and all testing is dependent on this parachute's arriving.
	\item \textbf{Finish the second airframe and have Kameron log more flight hours} (\textit{Ryan, Tyler C., Kameron}) \\
	Airframe \#2 is close to being completed. Kameron will attempt to fly airframe \#1 today. If necessary, we will incentivize Alex and Doug to assist more often with RC safety piloting.
	\item \textbf{Make progress on updating last year's vision GUI system and perform network range test with camera} (\textit{Tyler M., Jake J., Connor}) \\
	The main hiccup right now is getting the A6000 camera driver to build on the Odroid. Perhaps it comes down to getting things to build on a non-x86 processor.
\end{enumerate}

\section{Goals for the Coming Week}

The following is a list of our goals for the coming week, as well as details about how we plan to accomplish them:

\begin{enumerate}
	\item \textbf{Tune the autopilot and airspeed estimator} (\textit{Brady, John, Andrew})
	\item \textbf{Parachute deployment testing and iteration} (\textit{Jacob W., Derek, Brandon})
	\item \textbf{Finish the second airframe} (\textit{Ryan, Tyler C., Kameron})
	\item \textbf{Complete last year's vision GUI interop communication system and perform network range test with camera} (\textit{Tyler M., Jake J., Connor})
\end{enumerate}

\textbf{Please send us any feedback with regards to the progress we've made, as well as our plans for the coming week.}

% \newpage
% \begin{appendices}
%
%
%
% \end{appendices}

\end{document}
